---
title: "All VERA Variables"
format: html
---


```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r setup}
library(ggiraph)
library(dplyr)
library(ggplot2)
library(glue)
source("R/plot-utils.R")
#source("../R/ignore_sigpipes.R")
#ignore_sigpipe()


```

This page visualizes the baseline forecasts for all of the the VERA target variables.

## Most recent baseline forecasts for all variables {#sec-performance}

```{r}
config <- yaml::read_yaml("../challenge_configuration.yaml")

s3 <- arrow::s3_bucket(paste0(config$forecasts_bucket, "/bundled-summaries/project_id=", config$project_id, "/duration=P1D"), endpoint_override = config$endpoint, anonymous = TRUE)

# s3_scores <- arrow::s3_bucket(paste0(config$scores_bucket, "/project_id=", config$project_id, "/duration=P1D"), endpoint_override = config$endpoint, anonymous = TRUE)

s3_scores <- arrow::s3_bucket(file.path(paste0(config$scores_bucket), "bundled-parquet"), endpoint_override = config$endpoint, anonymous = TRUE)

reference_datetimes <-   duckdbfs::open_dataset(paste0("s3://",config$forecasts_bucket,
                                                     "/bundled-summaries/project_id=", 
                                                     config$project_id, "/duration=P1D"),
                                              s3_endpoint = "amnh1.osn.mghpcc.org",
                                              anonymous = TRUE) |> 
  #arrow::open_dataset(s3) |> 
  dplyr::group_by(variable) |> 
  #dplyr::mutate(reference_datetime_max = lubridate::as_datetime(as.Date(reference_datetime_max))) |> 
  dplyr::summarize(reference_datetime_max = max(reference_datetime)) |> 
  dplyr::collect() #|> 
  # dplyr::mutate(reference_datetime_max = lubridate::as_datetime(as.Date(reference_datetime_max) - lubridate::days(1))) # match baselines with other models

# reference_datetimes <- arrow::open_dataset(arrow::s3_bucket(config$summaries_bucket, endpoint_override = config$endpoint, anonymous = TRUE)) |> 
#   dplyr::filter(duration == 'P1D') |> 
#   dplyr::group_by(variable) |> 
#   dplyr::summarize(reference_datetime_max = max(reference_datetime)) |>  
#   dplyr::collect()

cutoff <- as.character(Sys.Date() - 30)

sites <- readr::read_csv(config$catalog_config$site_metadata_url, show_col_types = FALSE)

df <- duckdbfs::open_dataset(paste0("s3://",config$forecasts_bucket,
                                                     "/bundled-summaries/project_id=",
                                                     config$project_id, "/duration=P1D"),
                                              s3_endpoint = "amnh1.osn.mghpcc.org",
                                              anonymous = TRUE) |> 
  #arrow::open_dataset(s3) |> 
  # arrow::open_dataset(arrow::s3_bucket(config$summaries_bucket, endpoint_override = config$endpoint, anonymous = TRUE)) |> 
  # dplyr::filter(duration == 'P1D') |>
  filter(str_detect(model_id, "example", negate = TRUE)) |>
  left_join(reference_datetimes, by = "variable", copy = TRUE) |> 
  filter(reference_datetime == reference_datetime_max) |>
  left_join(sites, by = "site_id", copy = TRUE) |> 
  filter(site_id %in% sites$site_id) |> 
  # mutate(reference_datetime = lubridate::as_datetime(reference_datetime),
  #        datetime = lubridate::as_datetime(datetime)) |> 
  filter((depth_m == 1.6 & site_id == "fcre") | (depth_m == 1.5 & site_id == "bvre") | is.na(depth_m) |
         #depth_m == 0.1, lubridate::as_date(datetime) > lubridate::as_date(reference_datetime)) |> 
          depth_m == 0.1, datetime > reference_datetime) |> 

  #filter(model_id %in% c('climatology','persistenceRW')) |> 
  collect()

#reference_date <- max(lubridate::as_date(df$reference_datetime))
reference_date <- max(lubridate::as_date(df$reference_datetime) - lubridate::days(1))
```

Forecasts submitted on `r reference_date`

## Physical Variables 

::: panel-tabset
### Water temperature

```{r}
df |> 
  filter(variable == c("Temp_C_mean"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Temp (degC)')
```

### Dissolved oxygen

```{r}
if("DO_mgL_mean" %in% unique(df$variable)){
df |> 
  filter(variable == c("DO_mgL_mean"),
         site_id != 'tubr') |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'DO (mgL)')
}
```

### Dissolved oxygen saturation

```{r}
if("DOsat_percent_mean" %in% unique(df$variable)){
df |> 
  filter(variable == c("DOsat_percent_mean"),
         site_id != 'tubr') |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'DO_sat (%)')
}
```

### Secchi depth

```{r}
if("Secchi_m_sample" %in% unique(df$variable)){

df |> 
  filter(variable == c("Secchi_m_sample")) |>
    #filter(!model_id == 'secchi_last3obs_mean') |> ## remove KKH secchi model for now
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Secchi Depth (m)')
  
}
```

### Inflow discharge

```{r}
if("Flow_cms_mean" %in% unique(df$variable)){
df |> 
  filter(variable == c("Flow_cms_mean"))  |> 
    #filter(!model_id == 'persistenceRW') |> ## uncertainty is too high -- remove for now
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Flow (cms)')
}
```

### Conductivity

```{r}
if("SpCond_uScm_mean" %in% unique(df$variable)){
df |> 
  filter(variable == c("SpCond_uScm_mean"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Cond (uScm)')
}
```

### Turbidity

```{r}
if("Turbidity_FNU_mean" %in% unique(df$variable)){
df |> 
  filter(variable == c("Turbidity_FNU_mean"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Turbidity (FNU)')
}
```

### MOM binary

```{r}
if("MOM_binary_sample" %in% unique(df$variable)){
ggobj_df <- df |> 
filter(variable == c("MOM_binary_sample")) |> 
  mutate(observation = as.numeric(NA))
  
if(nrow(ggobj_df) > 0){

ggobj <- ggobj_df |> 
ggplot(aes(x = datetime, y = mean, color = model_id)) + 
  geom_line_interactive(aes(datetime, mean, col = model_id,
                              tooltip = model_id, data_id = model_id),
                        show.legend=TRUE) +
  facet_wrap(~site_id) +
  ylim(0,1) +
  labs(y = "Predicted probability") +
  theme_bw()

girafe(ggobj = ggobj,
         width_svg = 8, height_svg = 4,
         options = list(
           opts_hover_inv(css = "opacity:0.20;"),
           opts_hover(css = "stroke-width:2;"),
           opts_zoom(max = 4)
         ))
}
  }
```

### ThermoclineDepth_m_mean

```{r}
if("ThermoclineDepth_m_mean" %in% unique(df$variable)){
df |> 
  filter(variable == c("ThermoclineDepth_m_mean"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Depth (m)')
}
```

### SchmidtStability_Jm2_mean

```{r}
if("SchmidtStability_Jm2_mean" %in% unique(df$variable)){
df |> 
  filter(variable == c("SchmidtStability_Jm2_mean"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Stability (Jm2)')
}
```
:::




## Biological Variables

::: panel-tabset
### Chlorophyll-a

```{r}

if("Chla_ugL_mean" %in% unique(df$variable)){
df |> 
  filter(variable == c("Chla_ugL_mean")) |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Chla (ugL)')
}
```

### Chlorophyll-a bloom probability

```{r}

if("Bloom_binary_mean" %in% unique(df$variable)){
  
ggobj_df <- df |> 
  filter(variable == c("Bloom_binary_mean")) |> 
    mutate(observation = as.numeric(NA))
  
if(nrow(ggobj_df) > 0){

ggobj <- ggobj_df |> 
ggplot(aes(x = datetime, y = mean, color = model_id)) + 
  geom_line_interactive(aes(datetime, mean, col = model_id,
                              tooltip = model_id, data_id = model_id),
                        show.legend=TRUE) +
  facet_wrap(~site_id) +
  ylim(0,1) +
  labs(y = "Predicted probability") +
  theme_bw()

girafe(ggobj = ggobj,
         width_svg = 8, height_svg = 4,
         options = list(
           opts_hover_inv(css = "opacity:0.20;"),
           opts_hover(css = "stroke-width:2;"),
           opts_zoom(max = 4)
         ))
}
}
```

### Green Algae

```{r}
if("GreenAlgae_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("GreenAlgae_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Algae (ugL)')
}
```

### Bluegreen Algae

```{r}
if("Bluegreens_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("Bluegreens_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Algae (ugL)')
}
```

### Brown Algae

```{r}
if("BrownAlgae_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("BrownAlgae_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Algae (ugL)')
}
```

### Mixed Algae

```{r}
if("MixedAlgae_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("MixedAlgae_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Algae (ugL)')
}
```

### Green Algae DCM

```{r}
if("GreenAlgaeCM_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("GreenAlgaeCM_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Algae (ugL)')
}
```

### Bluegreen Algae DCM

```{r}
if("BluegreensCM_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("BluegreensCM_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Algae (ugL)')
}
```

### Brown Algae DCM

```{r}
if("BrownAlgaeCM_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("BrownAlgaeCM_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Algae (ugL)')
}
```

### Mixed Algae DCM

```{r}
if("MixedAlgaeCM_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("MixedAlgaeCM_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Algae (ugL)')
}
```

### DCM depth

```{r}
if("ChlorophyllMaximum_depth_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("ChlorophyllMaximum_depth_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Depth (m)')
}
```

### DCM binary

```{r}
if("DeepChlorophyllMaximum_binary_sample" %in% unique(df$variable)){
# df |> 
#   filter(variable == c("ChlorophyllMaximum_depth_sample"), 
#          site_id != 'tubr')  |> 
#     mutate(observation = as.numeric(NA)) |> 
#   forecast_plots_w_persistence(ylabel = 'Predicted probability')

ggobj_df <- df |> 
  filter(variable == "DeepChlorophyllMaximum_binary_sample") |> 
  mutate(observation = as.numeric(NA))
  
if(nrow(ggobj_df) > 0){

ggobj <- ggobj_df |> 
ggplot(aes(x = datetime, y = mean, color = model_id)) + 
  geom_line_interactive(aes(datetime, mean, col = model_id,
                              tooltip = model_id, data_id = model_id),
                        show.legend=TRUE) +
  facet_wrap(~site_id) +
  ylim(0,1) +
  labs(y = "Predicted probability") +
  theme_bw()

girafe(ggobj = ggobj,
         width_svg = 8, height_svg = 4,
         options = list(
           opts_hover_inv(css = "opacity:0.20;"),
           opts_hover(css = "stroke-width:2;"),
           opts_zoom(max = 4)
         ))
}
  }
  
```
:::




## Chemical Variables
::: panel-tabset

### fDOM

```{r}

if("fDOM_QSU_mean" %in% unique(df$variable)){

df |> 
  filter(variable == c("fDOM_QSU_mean"))  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'fDOM (QSU)')
}
```

### Dissolved methane

```{r}
if("CH4_umolL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("CH4_umolL_sample"),
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'CH4 (umolL)')
}
```

### Methane Flux

```{r}
if("CH4flux_umolm2s_mean" %in% unique(df$variable)){
df |> 
  filter(variable == c("CH4flux_umolm2s_mean"))  |> 
    #dplyr::mutate(duration = ifelse(model_id == 'persistenceRW', 'P1D', duration)) |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'CH4 Flux (umolm2s)')
}
```

### CO2 Flux

```{r}
if("CO2flux_umolm2s_mean" %in% unique(df$variable)){
df |> 
  filter(variable == c("CO2flux_umolm2s_mean"))  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'CO2 Flux (umolm2s)')
}
```

### Total N

```{r}
if("TN_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("TN_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Nitrogen (ugL)')
}
```

### Total P

```{r}
if("TP_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("TP_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Phosphorus (ugL)')
}
```

### NH4

```{r}
if("NH4_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("NH4_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Nitrogen (ugL)')
}
```

### NO3NO2

```{r}
if("NO3NO2_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("NO3NO2_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'Nitrogen (ugL)')
}
```

### SRP

```{r}
if("SRP_ugL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("SRP_ugL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'SRP (ugL)')
}
```

### DOC

```{r}
if("DOC_mgL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("DOC_mgL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'DOC (ugL)')
}
```

### Dissolved CO2

```{r}
if("CO2_umolL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("CO2_umolL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'CO2 (umolL)')
}
```

### Dissolved Silica

```{r}
if("DRSI_mgL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("DRSI_mgL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'DRSi (mgL)')
}
```

### DIC

```{r}
if("DIC_mgL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("DIC_mgL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'DIC (mgL)')
}
```

### Dissolved Carbon

```{r}
if("DC_mgL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("DC_mgL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'DC (mgL)')
}
```

### Dissolved Nitrogen

```{r}
if("DN_mgL_sample" %in% unique(df$variable)){
df |> 
  filter(variable == c("DN_mgL_sample"), 
         site_id != 'tubr')  |> 
    mutate(observation = as.numeric(NA)) |> 
  forecast_plots(ylabel = 'DN (mgL)')
}
```


:::
